---
title: "PA1_template"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Loading and preprocessing the data

```{r loading}
setwd("F:/js/R/ReproducibleResearch")
data<-read.csv("activity.csv")
```

##Ignore the missing values in the dataset
##Calculate the total number of steps taken per day

```{r }
datasplit<-split(data,as.factor(data$date))
total<-sapply(datasplit,function(x) sum(x$steps,na.rm = TRUE))
dates<-as.Date(names(total))
datatotal<-data.frame(dates,total,row.names = NULL)
```

##Make a histogram of the total number of steps taken each day
##of the total number of steps taken per day
```{r }
library(ggplot2)
plot1<-ggplot(datatotal,aes(x=datatotal$total))
plot1=plot1+geom_histogram()
print(plot1)
```

##Mean and median number of steps taken each day
```{r}
meantotalday<-mean(total)
mediantotalday<-median(total)
```

##Time series plot of the average number of steps taken
```{r}
datainterval<-split(data,as.factor(data$interval))
meaninterval<-sapply(datainterval,function(x) mean(x$steps,na.rm = TRUE))
meaninterval<-data.frame(data[1:288,3],meaninterval)
names(meaninterval)<-c("Intervals","MeanSteps")
plot2<-ggplot(meaninterval,aes(x=meaninterval$Intervals,y=meaninterval$MeanSteps))
plot2<-plot2+geom_line()+labs(x="Interval",y="mean steps ")
print(plot2)
```

##The 5-minute interval that, on average, contains the maximum number of steps
```{r}
maxinterval<-which.max(meaninterval$MeanSteps)
```

##Calculate and report the total number of missing values in the dataset
```{r}
missingdata<-sum(!complete.cases(data))
```

##Devise a strategy for filling in all of the missing values in the dataset
```{r}
d<-data[!complete.cases(data),]$interval
replacevalue<-as.numeric(sapply(d,function(x)meaninterval[which(meaninterval$Intervals==x),2]))
```

##Create a new dataset with the missing data filled in.
```{r}
setwd("F:/js/R/ReproducibleResearch")
datanew<-read.csv("activity.csv")
datanew[!complete.cases(datanew),]$steps<-replacevalue
```

##Histogram of the total number of steps taken each day after missing values are imputed
```{r}
datasplit2<-split(datanew,as.factor(datanew$date))
total2<-sapply(datasplit2,function(x) sum(x$steps,na.rm = TRUE))
dates2<-as.Date(names(total2))
datatotal2<-data.frame(dates2,total2,row.names = NULL)
plot3<-ggplot(datatotal2,aes(x=datatotal2$total2))
plot3=plot3+geom_histogram()
print(plot3)
```

##Mean and median number of steps taken each day
```{r}
meantotalday2<-mean(total2)
mediantotalday2<-median(total2)
```

##Create a new factor variable in the dataset with two level
```{r}
datanew$date<-as.Date(datanew$date)
weekday<-sapply(datanew$date,function(x){
  if(weekdays(x) %in% c("ÐÇÆÚÁù" ,"ÐÇÆÚÈÕ")) 
  {y=0}
  else{y=1}})
datanew<-data.frame(datanew,weekday)
```

##Panel plot 
```{r}
dataweekday<-split(datanew,as.factor(datanew$weekday))
datainterval2<-split(dataweekday[[1]],as.factor(dataweekday[[1]]$interval))
meaninterval2<-sapply(datainterval2,function(x) mean(x$steps,na.rm = TRUE))
meaninterval2<-data.frame(data[1:288,3],meaninterval2)
names(meaninterval2)<-c("Intervals","MeanSteps")
datainterval3<-split(dataweekday[[2]],as.factor(dataweekday[[2]]$interval))
meaninterval3<-sapply(datainterval3,function(x) mean(x$steps,na.rm = TRUE))
m<-data.frame(meaninterval2,meaninterval3)
names(m)<-c("Intervals","MeanStepsOnWeekends","MeanStepsOnWorkdanys")
par(mfrow=c(2,1),mar=c(2,4,1,1))
plot(m$Intervals,m$MeanStepsOnWeekends,ylab = "meansteps",type="l",main="weekends")
plot(m$Intervals,m$MeanStepsOnWorkdanys,ylab = "meansteps",type="l",main="workdays")
```
